Learning constraints in tabular data

### 2016-05-13 Paper/ECAI/tabular.tex
moved on of the figures

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}

@@

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{figure*}

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, cf. \cite{luc_book}. This is because constraints may be logically equivalent or may be implied by other constraints.

@@

\paragraph{Example}
Consider the following implication:
$$\ecperm{G} \rightarrow \ecalldiff{G}$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $ALLDDIFFERENT(G)$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@

\begin{figure}
  {\small
    \begin{align*}
      & SERIES(\range{T_{1}}{\rangeall}{1}) \\
%
      & \ecrank{\range{T_{1}}{\rangeall}{8}}{\range{T_{1}}{\rangeall}{7}} \\
%
      & \ecsumc{\range{T_{2}}{1}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecsumc{\range{T_{6}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecsumr{\range{T_{1}}{\rangeall}{7}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      & \ecaggc{AVERAGE}{\range{T_{2}}{2}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MAX}{\range{T_{2}}{3}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggc{MIN}{\range{T_{2}}{4}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      & \ecaggif{SUM}{\range{T_{1}}{\rangeall}{10}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \ecaggif{MAX}{\range{T_{1}}{\rangeall}{11}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      & \eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}} \\
%
      & \range{T_{6}}{\rangeall}{4} = PREV(\range{T_{6}}{\rangeall}{4}) + \range{T_{6}}{\rangeall}{2} - \range{T_{6}}{\rangeall}{3}
    \end{align*}
  }
  \caption{Constraints that are satisfied in the case study (Figure~\ref{fig:main_example}) and expected to be found by our implementation. Functional constraint are omitted.}
  \label{fig:sol_example}
\end{figure}

>>>>

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{subcaption}

@@

\begin{figure*}[thb]

  \begin{subfigure}{.70\textwidth}
  \begin{center}
    \includegraphics[width=1\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{subfigure}
\hfill
\begin{subfigure}{.30\textwidth}
  {\small
    \begin{align*}
      &~\ecseries{\range{T_{1}}{\rangeall}{1}} \\
%
      &~\ecrank{\range{T_{1}}{\rangeall}{8}}{\range{T_{1}}{\rangeall}{7}} \\
%
      &~\ecsumc{\range{T_{2}}{1}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      &~\ecsumc{\range{T_{6}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      &~\ecsumr{\range{T_{1}}{\rangeall}{7}}{\range{T_{1}}{\rangeall}{\rangeto{3}{6}}} \\
%
      &~\ecaggc{AVERAGE}{\range{T_{2}}{2}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      &~\ecaggc{MAX}{\range{T_{2}}{3}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      &~\ecaggc{MIN}{\range{T_{2}}{4}{\rangeall}}{\range{T_{1}}{\rangeall}{\rangeto{3}{7}}} \\
%
      &~\ecaggif{SUM}{\range{T_{1}}{\rangeall}{10}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      &~\ecaggif{MAX}{\range{T_{1}}{\rangeall}{11}}{\range{T_{5}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}}{\range{T_{5}}{\rangeall}{2}} \\
%
      &~\eclookup{\range{T_{4}}{\rangeall}{3}}{\range{T_{4}}{\rangeall}{2}}{\range{T_{1}}{\rangeall}{1}}{\range{T_{1}}{\rangeall}{2}} \\
%
      &~\range{T_{6}}{\rangeall}{4} = PREV(\range{T_{6}}{\rangeall}{4}) + \range{T_{6}}{\rangeall}{2} - \range{T_{6}}{\rangeall}{3}
    \end{align*}}
  \vspace{-10pt}
  \caption{Constraints that are satisfied in the case study (Figure on the left) and expected to be found by our implementation. Functional constraint are omitted.}
  \label{fig:sol_example}
\end{subfigure}
\end{figure*}

@@

Depending on the application, a solution to the tabular constraint learning problem may contain \textit{redundant} constraints, for details we refer to relational learning literature \cite{luc_book}. This is because constraints may be logically equivalent or may be implied by other constraints.

@@

\paragraph{Example}
Consider the following implication:
$$\ecperm{G} \rightarrow \ecalldiff{G}$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $\ecdiff{G}$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@
